\begin{abstract}
Today machine learning is entering many business and scientific applications.
The life cycle of machine learning applications consist of data preprocessing for transforming the raw data into features, training a model using the features, and deploying the model for answering prediction queries.
In order to guarantee accurate predictions, one has to continuously monitor and update the deployed models and pipelines. 
Current deployment platforms update the models using online learning methods.
When online learning alone is not adequate to guarantee the prediction accuracy, some deployment systems provide a mechanism for automatic or manual retraining the model.
While the online training is fast, the retraining of the model is time-consuming and adds extra overhead and complexity to the process of deployment.

We propose a novel continuous deployment approach for updating the deployed model using a combination of the incoming real-time data and the historical data.
We utilize fast sampling techniques to include the historical data in the training process, thus eliminating the need for complete retraining of deployed model.
Moreover, we offer several optimizations such as online statistics computation and materialization of preprocessed features to minimize the total training and data preprocessing time.
In our experiments, we deploy two pipelines and models using different datasets.
We show that the continuous deployment reduces the total training cost up to 13 times over the state-of-the-art deployment approaches.
\todo[inline]{We don't want to send the message that continuous deployment is always better than periodical. That's why I add "In some cases", even though for both of the datasets we are getting a better quality.}
In some cases, continuous deployment also improves the error rate (up to 0.3\%) over the state-of-the-art deployment approaches.
\end{abstract}